\mytitle

### 2016-06-19 pdocs/thesis/article-section-2.tex
typo fixes and other small tunings

Velocity-based formulation is not typically used in structural or mechanical engineering.
 \citet[p.~45]{erleben.thesis} provides reasoning and theoretical details why it is so popular in 
constraint-based rigid body simulation. 
Main reason is that collision handling can be done without additional procedures.
In structural finite element analysis solution method is selected carefully based on needed features.
In most cases static small displacement solution using displacement based boudary conditions is used.
For large displacement static analysis analysis loading is applied in substeps and 
displacements are used to update element mesh.
Further enhancements are material nonlinearity and dynamic analysis.
Physics engine provides dynamic analysis with large displacements.

>>>>

Velocity-based formulation is not typically used in structural or mechanical engineering.
 \citet[p.~45]{erleben.thesis} provides reasoning and theoretical details why it is so popular in 
constraint-based rigid body simulation. 
Main reason is that collision handling can be done without additional procedures.
In structural analysis solution method is selected carefully based on needed features.
For most complex scenarios finite element method is used.
In most cases static small displacement solution using displacement based boundary conditions is used.
For large displacement static analysis analysis loading is applied in substeps and 
displacements are used to update element mesh.
Further enhancements are material nonlinearity and dynamic analysis.
Physics engine provides dynamic analysis with large displacements.
